---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(phenotools)
```

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(file.path(getwd(),"inst","rstudio","templates", "phenotools.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;')
```

# phenotools

The goal of this package is to allow researchers to use phenotypic data from MoBa and linked registry sources reproducibly and efficiently. 

## Installation

You can install the latest working version of phenotools from source as follows...

```{r install, echo=TRUE, eval= FALSE}
install.packages()
```

At present, any missing dependencies need to be installed manually from the TSD CRAN copy, i.e.,

```{r dependencies, echo=TRUE, eval= FALSE}
install.packages()
```

## Overview and project set-up

The package primarily provides functions to assist you at the beginning and end of your analytic workflow; specifically, in the respective areas of data preparation, and analysis documentation and reporting. These are outlined below. However, to make full usage of the phenotools package, it is advisable to begin by using it to set up your analytic project with a pre-defined structure using the `initialise_project` function:

## Data preparation with phenotools




## Analysis documentation and reporting with phenotools (in development)
